Letter to Reviewers of Submission \#341

### 2015-06-27 relatedwork.tex
fixed widow
within page limits! still writing revision letter

\begin{figure*}
\centering
\includegraphics[width=.9\linewidth]{fig/system/system.pdf}
\caption{\label{fig:system}A diagram of RCloud's architecture. }
\end{figure*}

@@

There has been noteworthy work on specific techniques
to support collaborative or social code development and data analysis,
such as social bookmarking \cite{Millen:2006:DSB} \cite{Heer:2007:VAV}
and crowdsourcing \cite{Fast:2014:ECS}.
Similarly, there are computational methods to support high
performance execution in incremental code development
environments \cite{Guo:2010:TPI}.
The goal of RCloud is to define an environment in which many such
techniques may be integrated and made available to a broad community.
\begin{figure*}
\centering
\includegraphics[width=.95\linewidth]{fig/notebook/notebook.pdf}
\caption{\label{fig:notebook}An RCloud notebook is a sequence of
\emph{cells}, each a snippet of source in one of the supported languages (typically R, but Python and others are also supported) or Markdown. The main creation workflow involves editing notebooks, which are transparently stored as git repositories in GitHub, providing us with easy access to primitives for version tracking. Notebooks can be executed as they're edited (left), or in a standalone viewer (right), via a slightly different URL. This provides a lightweight, low-friction mechanism for sharing results which we discuss in detail in Section~\ref{sec:interviews}. }
\end{figure*}

One high-level goal is to reduce the gap between implementers and
deployers in visual analytics. The fusion of development with
production operations in software release management (``DevOps''
\cite{Httermann:2012:DD} or ``continuous integration''
\cite{Fowler:2006:Continuous}) is a trend in web services and similar
fields.
%% By making it convenient for data scientists to expend just a
%% little additional effort when creating experiments, we may be able to
%% eliminate the need for programming teams to recreate their work to
%% deploy it in production, which has a high cost in time, expense and
%% accuracy.
%gw{sentence was just too long}
When programming teams recreate the work of data scientists to
deploy it in production, it has a high cost in time, expense and
accuracy. By making it convenient for data scientists to productionize
their experiments, we may be able to eliminate the need for this costly step.

>>>>

\begin{figure*}
\centering
\includegraphics[width=.9\linewidth]{fig/system/system.pdf}
\caption{\label{fig:system}A diagram of RCloud's architecture. RCloud was specifically designed to leverage existing systems and standards, and so communication between most parts of the system happens through HTTP. As a result, some desirable features of RCloud become natural, such as native support for RCloud notebooks as web services. }
\end{figure*}

@@

There has been noteworthy work on specific techniques
to support collaborative or social code development and data analysis,
such as social bookmarking \cite{Millen:2006:DSB} \cite{Heer:2007:VAV}
and crowdsourcing \cite{Fast:2014:ECS}.
Similarly, there are computational methods to support high
performance execution in incremental code development
environments \cite{Guo:2010:TPI}.
The goal of RCloud is to define an environment in which many such
techniques may be integrated and made available to a broad community.
\begin{figure*}
  \vspace{-1.5em}
\centering
\includegraphics[width=.95\linewidth]{fig/notebook/notebook.pdf}
  \vspace{-1.5em}
\caption{\label{fig:notebook}An RCloud notebook is a sequence of
\emph{cells}, each a snippet of source in one of the supported languages (typically R, but Python and others are also supported) or Markdown. The main creation workflow involves editing notebooks, which are transparently stored as git repositories in GitHub, providing us with easy access to primitives for version tracking. Notebooks can be executed as they're edited (left), or in a standalone viewer (right), via a slightly different URL. This provides a lightweight, low-friction mechanism for sharing results which we discuss in detail in Section~\ref{sec:interviews}. }
  \vspace{-1.5em}
\end{figure*}

One high-level goal is to reduce the gap between implementers and
deployers in visual analytics. The fusion of development with
production operations in software release management (``DevOps''
\cite{Httermann:2012:DD} or ``continuous integration''
\cite{Fowler:2006:Continuous}) is a trend in web services and similar
fields.
%% By making it convenient for data scientists to expend just a
%% little additional effort when creating experiments, we may be able to
%% eliminate the need for programming teams to recreate their work to
%% deploy it in production, which has a high cost in time, expense and
%% accuracy.
%gw{sentence was just too long}
When programming teams recreate the work of data scientists to
deploy it in production, it has a high cost in time, expense and
accuracy. By making it convenient for data scientists to productionize
experiments, we may be able to eliminate the need for this costly step.
